---
title: "About Me"
toc: true
format: 
  html:
    code-fold: true
    code-summary: "View Code"
---

## Professional Background

I graduated from the University of California, Santa Barbara in 2022 with a B.S. in Zoology. During that time, I contributed to a meta-analysis, extracting data on ungulate diets to better understand how specific functional traits of ungulates influence plant biodiversity. After graduating, I held various positions within the public sector, working for the National Parks Service and the California Department of Food and Agriculture.

I went on to receive my Master of Environmental Data Science at the UC Santa Barbara, Bren School of Environmental Science & Management. I am currently completing a manuscript that evaluates the effectiveness of machine learning methods for predicting species distributions, using long-term data on the Black-Bellied Slender Salamander (*Batrachoseps nigriventris*).

## Education

Master of Environmental Data Science - University of California, Santa Barbara (2024)

B.S. Zoology - University of California, Santa Barbara (2022)

## Bird Watching

One of my favorite undergraduate classes was my vertebrate lab. I had the opportunity to visit sites across Santa Barbara to go bird watching, and learn about wildlife surveying techniques. I have continued to bird watch ever since, and keep track of my sightings using the Merlin and eBird apps, which are maintained by the [Cornell Lab of Ornithology.](https://www.birds.cornell.edu/home/)

I thought it would be fun to visualize my personal bird sightings using a `leaflet` map:

```{r, results='hide', echo=FALSE, message = FALSE, warning = FALSE}
# libraries
library(tidyverse)
library(janitor)
library(here)
library(leaflet)
library(sf)

# read data
birds <- read_csv('life-list/ebird_world_life_list.csv') %>% 
  clean_names() %>% #clean col names
  filter(countable != 0) #remove obs that don't count
```

```{r, echo=FALSE}
# add latitude, longitude points
birds <- birds %>%
  mutate(lat_long = case_when(location == "Alice Keck" ~ 
                                "34.429166_-119.705992",
                              
                              location == "Apt" ~
                                "34.415086_-119.857020",

                              location == "Bragg Botanical Garden" ~
                                "39.409404_-123.809236",

                              location == "Bridalveil Straight" ~
                                "37.719070_-119.648158",

                              location == "Campus Beach" ~
                                "34.408739_-119.842396",

                              location == "Castle Rock" ~
                                "38.989404_-119.908882",

                              location == "CCBER" ~
                                "34.419488_-119.855371",

                              location == "CRZ Plains" ~
                                "35.195162_-119.860073",

                              location == "CRZ Plains 2" ~
                                "35.195162_-119.860073",

                              location == "Dev Slough" ~
                                "34.408242_-119.877595",

                              location == "Eagle Energy" ~
                                "34.952157_-120.451558",

                              location == "Grove" ~
                                "34.420159_-119.851430",

                              location == "Indian Village" ~
                                "37.748998_-119.587949",

                              location == "Lagoon" ~
                                "34.411366_-119.850344",
                              
                              location == "Lake Los Carneros" ~
                                "34.441389_-119.851803",
                              
                              location == "Lake Los Carneros (water)" ~
                                "34.441841_-119.848191",
                              
                              location == "Lake Los Carneros 2" ~
                                "34.441389_-119.851803",
                              
                              location == "Lover's Loop Trail" ~
                                "34.741097_-120.062162",
                              
                              location == "MN House" ~
                                "34.184626_-119.186175",
                              
                              location == "Monterrey-aquaroum" ~
                                "36.618565_-121.901439",
                              
                              location == "Mugu Beach" ~
                                "34.109835_-119.123004",
                              
                              location == "Mugu Park 2" ~
                                "34.126372_-119.094583",
                              
                              location == "Music Library" ~
                                "34.413062_-119.849671",
                              
                              location == "NBVC Soccer Field" ~
                                "34.184626_-119.186175",
                              
                              location == "Oxn" ~
                                "34.184626_-119.186175",
                              
                              location == "Psych Building" ~
                                "34.413062_-119.849671",
                              
                              location == "SB Pistachio" ~
                                "34.847064_-119.481744",
                              
                              location == "sb-zoo-natives" ~
                                "34.420662_-119.665089",
                              
                              location == "Soda Lake" ~
                                "35.195162_-119.860073",
                              
                              location == "Sup House" ~
                                "37.741642_-119.599128",
                              
                              location == "Tiffany Park" ~
                                "34.952157_-120.451558",
                              
                              location == "Traffic Management Office" ~
                                "37.741642_-119.599128",
                              
                              location == "Ventura Settling Ponds" ~
                                "34.237653_-119.262575",
                              
                              location == "Vet Resource Center" ~
                                "34.413062_-119.849671",
                              
                              location == "Willoeglen Park" ~
                                "34.450331_-119.744329",
                              
                              location == "YOS 22 Apt" ~
                                "37.672375_-119.807656")) %>% 
  
  separate(lat_long, into = c("latitude", "longitude"),
           sep = "_", convert = TRUE)
```

```{r, echo=FALSE}
## === Preparation ===
# add CRS
birds <- birds %>%   
  st_as_sf(coords = c('longitude', 'latitude'), crs = 'EPSG:4236')

# create icon path and token
source(here("life-list", "token.R"))
iconpath <- here('life-list/bird-icon.png')
```

```{r, warning=FALSE}
# add CRS to lat/long points
birds <- birds %>%   
  st_as_sf(coords = c('longitude', 'latitude'), crs = 'EPSG:4236')

# create map
birds %>% 
  leaflet() %>% 
  addProviderTiles(providers$Jawg.Streets,
                   options = providerTileOptions(accessToken = token)) %>% 
  addMarkers(label = birds$common_name,
             popup = paste0(birds$common_name, ' (',
                            birds$scientific_name, ')'),
             clusterOptions = markerClusterOptions(),
             icon = makeIcon(iconUrl = iconpath,
                             iconWidth = 32, iconHeight = 32))
```
