---
title: "About Me"
toc: true
format: 
  html:
    code-fold: true
    code-summary: "View Code"
---

## Professional Background

I graduated from the University of California, Santa Barbara in 2022 with a B.S. in Zoology. During that time, I assisted in a meta-analysis, extracting global data on ungulate diets to better understand how plant biodiversity is affected by select functional traits of large herbivores. After graduating, I held various positions within the public sector, working for the National Parks Service and later, the California Department of Food and Agriculture.\
\
I am currently pursuing a Master of Environmental Data Science at the UC Santa Barbara, Bren School of Environmental Science & Management. Moving forward, I hope to use spatial data to assess landscape changes, and the impact of ecosystem stressors including climate change, disease, and invasive species.

## Education

Master of Environmental Data Science - University of California, Santa Barbara (Expected June 2024)

B.S. Zoology - University of California, Santa Barbara (2022)

## Bird Watching

One of my favorite undergraduate classes was my vertebrate lab. I had the opportunity to visit sites across Santa Barbara to go bird watching, and learn about wildlife surveying techniques. I have continued to bird watch ever since, and keep track of my sightings using the Merlin and eBird apps, which are maintained by the [Cornell Lab of Ornithology.](https://www.birds.cornell.edu/home/)

I thought it would be fun to visualize my personal bird sightings using a `leaflet` map:

```{r, results='hide', echo=FALSE, message = FALSE, warning = FALSE}
# libraries
library(tidyverse)
library(janitor)
library(here)
library(leaflet)
library(sf)

# read data
birds <- read_csv('life-list/ebird_world_life_list.csv') %>% 
  clean_names() %>% #clean col names
  filter(countable != 0) #remove obs that don't count
```

```{r, echo=FALSE}
# add latititudes
birds <- birds %>% 
  mutate(latitude = case_when(location == 'Alice Keck' ~ '34.429166',
                              location == 'Apt' ~ '34.415086',
                              location == 'Bragg Botanical Garden' ~ '39.409404',
                              location == 'Bridalveil Straight' ~ '37.719070',
                              location == 'Campus Beach' ~ '34.408739',
                              location == 'Castle Rock' ~'38.989404',
                              location == 'CCBER' ~ '34.419488',
                              location == 'CRZ Plains' ~ '35.195162',
                              location == 'CRZ Plains 2' ~ '35.195162',
                              location == 'Dev Slough' ~ '34.408242',
                              location == 'Eagle Energy' ~ '34.952157',
                              location == 'Grove' ~ '34.420159',
                              location == 'Indian Village' ~ '37.748998',
                              location == 'Lagoon' ~ '34.411366',
                              location == 'Lake Los Carneros' ~ '34.441389',
                              location == 'Lake Los Carneros (water)' ~ '34.441841',
                              location == 'Lake Los Carneros 2' ~ '34.441389',
                              location == "Lover's Loop Trail" ~ '34.741097',
                              location == 'MN House' ~ '34.184626',
                              location == 'Mugu Beach' ~ '34.109835',
                              location == 'Mugu Park 2' ~ '34.126372',
                              location == 'Music Library' ~ '34.413062',
                              location == 'NBVC Soccer Field' ~ '34.184626',
                              location == 'Oxn' ~ '34.184626',
                              location == 'Psych Building' ~ '34.413062',
                              location == 'SB Pistachio' ~ '34.847064',
                              location == 'sb-zoo-natives' ~ '34.420662',
                              location == 'Soda Lake' ~ '35.195162',
                              location == 'Sup House' ~ '37.741642',
                              location == 'Tiffany Park' ~ '34.952157',
                              location == 'Traffic Management Office' ~ '37.741642',
                              location == 'Vet Resource Center' ~ '34.413062',
                              location == 'Willoeglen Park' ~ '34.450331',
                              location == 'YOS 22 Apt' ~ '37.672375'))
```

```{r, echo=FALSE}
# add longitudes
birds <- birds %>% 
  mutate(longitude = case_when(location == 'Alice Keck' ~ '-119.705992',
                        location == 'Apt' ~ '-119.857020',
                        location == 'Bragg Botanical Garden' ~ '-123.809236',
                        location == 'Bridalveil Straight' ~ '-119.648158',
                        location == 'Campus Beach' ~ '-119.842396',
                        location == 'Castle Rock' ~'-119.908882',
                        location == 'CCBER' ~ '-119.855371',
                        location == 'CRZ Plains' ~ '-119.860073',
                        location == 'CRZ Plains 2' ~ '-119.860073',
                        location == 'Dev Slough' ~ '-119.877595',
                        location == 'Eagle Energy' ~ '-120.451558',
                        location == 'Grove' ~ '-119.851430',
                        location == 'Indian Village' ~ '-119.587949',
                        location == 'Lagoon' ~ '-119.850344',
                        location == 'Lake Los Carneros' ~ '-119.851803',
                        location == 'Lake Los Carneros (water)' ~ '-119.848191',
                        location == 'Lake Los Carneros 2' ~ '-119.851803',
                        location == "Lover's Loop Trail" ~ '-120.062162',
                        location == 'MN House' ~ '-119.186175',
                        location == 'Mugu Beach' ~ '-119.123004',
                        location == 'Mugu Park 2' ~ '-119.094583',
                        location == 'Music Library' ~ '-119.849671',
                        location == 'NBVC Soccer Field' ~ '-119.186175',
                        location == 'Oxn' ~ '-119.186175',
                        location == 'Psych Building' ~ '-119.849671',
                        location == 'SB Pistachio' ~ '-119.481744',
                        location == 'sb-zoo-natives' ~ '-119.665089',
                        location == 'Soda Lake' ~ '-119.860073',
                        location == 'Sup House' ~ '-119.599128',
                        location == 'Tiffany Park' ~ '-120.451558',
                        location == 'Traffic Management Office' ~ '-119.599128',
                        location == 'Vet Resource Center' ~ '-119.849671',
                        location == 'Willoeglen Park' ~ '-119.744329',
                        location == 'YOS 22 Apt' ~ '-119.807656'))
```

```{r, echo=FALSE}
## === Preparation ===
# add CRS
birds <- birds %>%   st_as_sf(coords = c('longitude', 'latitude'), crs = 'EPSG:4236')

# create icon path and token
token <- 'Wrbj5TCS0i2D12kEn3oWNQcAWfTsF6eFF31F67I2o2QhgEXReZOemCghmyeR7j6Z'
iconpath <- here('life-list/bird-icon.png')
```

```{r, warning=FALSE}
# add CRS to lat/long points
birds <- birds %>%   st_as_sf(coords = c('longitude', 'latitude'), crs = 'EPSG:4236')

# create map
birds %>% 
  leaflet() %>% 
  addProviderTiles(providers$Jawg.Streets,
                   options = providerTileOptions(accessToken = token)) %>% 
  addMarkers(label = birds$common_name,
             popup = paste0(birds$common_name, ' (',
                            birds$scientific_name, ')'),
             clusterOptions = markerClusterOptions(),
             icon = makeIcon(iconUrl = iconpath,
                             iconWidth = 32, iconHeight = 32))
```
